 Austral Spring Extratropical Southern Hemisphere zonally assymetric circulation

### 2021-06-01 analysis/paper/shceof.Rmd
Cambia método PSA
Closes #43

We computed the level-dependent Southern Annular Mode (SAM) index as the leading EOF of year-round monthly geopotential height anomalies south of 20ºS at each level for the whole period [@baldwin2009].
We further split the SAM into its zonally symmetric and zonally asymmetric components (S-SAM and A-SAM indices respectively).
These indices were obtained by projecting the zonally asymmetric and zonally symmetric part of the SAM spatial pattern onto monthly geopotential height fields, as proposed by @campitelli2021.
The Pacific South American patterns (PSA1 and PSA2) were calculated as the third and fourth leading EOF of seasonal mean for 500 hPa geopotential height combining all seasons following @mo2001.

>>>>

We computed the level-dependent Southern Annular Mode (SAM) index as the leading EOF of year-round monthly geopotential height anomalies south of 20ºS at each level for the whole period [@baldwin2009].
We further split the SAM into its zonally symmetric and zonally asymmetric components (S-SAM and A-SAM indices respectively).
These indices were obtained by projecting the zonally asymmetric and zonally symmetric part of the SAM spatial pattern onto monthly geopotential height fields, as proposed by @campitelli2021.
The Pacific South American patterns (PSA1 and PSA2) were calculated following @mo2001 as the third and fourth leading EOF of seasonal mean anomalies for SH 500 hPa geopotential height combining all seasons.
